---
title: "Bonus"
author: "Chhiring Lama, Kate Colvin, Yuying Lu"
date: "2024-12-03"
output: html_document
---

```{r setup, include=FALSE, message = FALSE}
library(tidyverse)
library(here)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "85%", 
	fig.align = "center"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

Using `projectr`:
```{r}
#devtools::install_github("jeff-goldsmith/projectr")
library(projectr)
#projectr::proj_start(proj_dir = "~/Work/temp_project", 
  #                   data_dir = "~/Data/temp_data")
```


Using `here` to import files
```{r}
a <- data <- read_csv(here("~/Library/CloudStorage/OneDrive-ColumbiaUniversityIrvingMedicalCenter/Course Materials/Fall 2024/Data Science 1/20241107_linear_models/data/", "nepalese_children.csv"))
```



Using regression
```{r}
data("mtcars")

with(mtcars, t.test(mpg[ am == 0], mpg[am ==1])) |> 
  broom::tidy()

t.test(mpg ~ am, data = mtcars) |> 
  broom::tidy()

lm(mpg ~ am, data = mtcars) |> 
  broom::tidy()
```

Plot using the relationship between am and mpg
```{r}
ggplot(aes(group = am, y = mpg), data = mtcars) +
  geom_boxplot()
```


Some LLMs that to consider (not the most intuitive on a day to day basis, need to double check )

- Github Copilot: https://copilot.github.com/. What does Copilot do? "It helps you write code faster and with fewer errors. It draws context from the code you’re working on, suggesting whole lines or entire functions. It’s a great tool for pair programming, code reviews, and writing code faster." written by copilot

- chatgpt: "https://chat.openai.com/. What does ChatGPT do? "ChatGPT is a large language model trained to generate human-like responses to given prompts. It can be used for a variety of tasks, such as generating conversational responses, answering questions, and providing recommendations." written by chatgpt". 




